Incremental λ-Calculus in Cache-Transfer Style

### 2017-08-22 popl18/transformation.tex
Cosmetics.

By the first rule, $\compile{\param}$ maps each source toplevel definition
``$\tf = \slam{\tx}{\sterm}$'' to the compiled code of the
function $\tf$ and to the derivative~$\tdf$ of~$\tf$ expressed in the
target language~$\target$. These target definitions are generated by a
first call to the compilation function~$\compileterm{\tcachecons\temptycache\tx}{\sterm}$:
it returns both~$\tterm$, the compiled body of $\tf$ and the
cache term~$\tcache$ which contains the names of the intermediate
values computed by the evaluation of $\tterm$. This cache
term~$\tcache$ is used as a cache pattern to define the second
argument of the derivative of $\tf$. That way, we make sure that the
shape of the cache expected by $\tdf$ is consistent with the shape of
the cache produced by $\tf$. Derivative body~$\tdf$ is
computed by derivation call~$\derive{\tcachecons\temptycache{(\tchange{\tx}{\tdx})}}{\sterm}$.

>>>>

By the first rule, $\compile{\param}$ maps each source toplevel definition
``$\tf = \slam{\tx}{\sterm}$'' to the compiled code of the
function $\tf$ and to the derivative~$\tdf$ of~$\tf$ expressed in the
target language~$\target$. These target definitions are generated by a
first call to the compilation function~$\compileterm{\tcachecons\temptycache\tx}{\sterm}$:
it returns both~$\tterm$, the compiled body of~$\tf$ and the
cache term~$\tcache$ which contains the names of the intermediate
values computed by the evaluation of~$\tterm$. This cache
term~$\tcache$ is used as a cache pattern to define the second
argument of the derivative of~$\tf$. That way, we make sure that the
shape of the cache expected by~$\tdf$ is consistent with the shape of
the cache produced by~$\tf$. Derivative body~$\tdf$ is
computed by derivation call~$\derive{\tcachecons\temptycache{(\tchange{\tx}{\tdx})}}{\sterm}$.
